---
title: "wk9-homework-lastname-firstname"
author: "Mahim Naveed"
date: "November 22, 2015"
output: html_document
---

#### 1. Initial GitHub workflow

a. Pat yourselves on the back if you were able to "fork", then "clone" this repo. Maybe massage your brain, too.

b. Re-save this file with your last and first name as well as altering the title of this file.

#### Tips for creating functions

*Use the least possible number of steps. Work line by line, printing out each value as you create the function. Trying to create a function that will solve the whole problem will typically lead to long debugging times because you will not know where you made the mistake.*

#### 2. if-then-else
Create a function `is.a.number()` that takes a single parameter `X` and returns `"Is a number"` if it is a number, `"Is NA"` if it is an `NA` value, and `"I have no clue"` if it is neither a number nor an `NA` value. Use the `is.na()` and `is.numeric()` functions.

```{r}
is.a.number <- function(x) {
  if(is.numeric(x)) {"Is a number"}
  else if(is.na(x)) {"NA"}
  else {"I have no clue"}
}

#testing
is.a.number(597)
is.a.number(NA)
is.a.number("mahim")
```


#### 3. primes 
Create a function that when inputting a single prime number between 3 and 100, it will output a `TRUE` or `FALSE` in a `message()`. Insert an error message as if somebody were to insert a number less than 3, greater than 100, or a non-numeric character. (*Please don't insert all of the prime numbers between 3 and 100 into the function...*)

```{r}
prime.func <- function(x) {
 if(x < 3 | x > 100 | is.numeric(x)==FALSE)
    stop("Invalid input")
  if (x==3) {TRUE}
  else if (any(x %% 3:(x-1) == 0)) {FALSE}
  else {TRUE}
}

#testing
prime.func(1)
prime.func(3)
prime.func(43)
prime.func(100)
prime.func(101)
prime.func("mahim")
```


#### 4. ggplot2

a. Using `ggplot2`, create a function that when inputting a single continuous variable, it will print out a histogram. Include arguments to alter the theme, x-variable label, a title, and a `TRUE` or `FALSE` option to create a density plot.

```{r}
my.func<- function(x, ...) {
require(ggplot2)
p <- qplot(x, ... , geom="histogram", binwidth=0.1,
      colour = I("blue"), size = I(0.5), ylab="Frequency", 
      xlab="Continuous Variable Label", main="Title") 
#density(x, ..., add=FALSE))
print(p)
}

#testing
my.func(movies$rating)
```




b. Similarly, create a function that when inputting two continuous variables, it will print a scatterplot. Additionally, in the console, print the mean and variance of the two variables as well as the coefficient value of the specified x-variable.  Include arguments to alter the title and a `TRUE` or `FALSE` option to include a smoothing method of *lm* aka a simple linear model line in/on the scatterplot.

```{r}
my.func<- function(x, ...) {
require(ggplot2)
p <- qplot(x, ... , geom="histogram", binwidth=0.1,
      colour = I("blue"), size = I(0.5), ylab="Frequency", 
      xlab="Continuous Variable Label", main="Title") 
#density(x, ..., add=FALSE))
print(p)
}

#testing
my.func(movies$rating)

```


#### 5. Remaining GitHub workflow

a. Now finish off the workflow of submitting your homework by "committing" the changes locally, "pushing" the changes to YOUR online repo, and finally creating a pull request. 

b. Pat yourselves on the back, again.  You deserved it.
